---
title: "Fine Amount"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
    theme: cosmo
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

source("code/data_cleaning.R")
source("code/formatting.R")
```

##### Fine Amount {.tabset}

###### Payment Amount by Borough

```{r}
payment_by_borough <- violation %>% filter(payment_amount != 0)
fig1 <- plot_ly(payment_by_borough, x = ~payment_amount, color = ~borough, type = "box", colors = "viridis")
fig1 %>% layout(yaxis = list(showticklabels = FALSE),
               title = "<b>Payment by Borough</b>",
                xaxis = list(title = "Payment Amount"))
```

We see that the median payment amount is approximately the same across the five boroughs, around $60-65. However, it seems that the payment amount distributions in the Bronx, Brooklyn, and Manhattan all have a significant right skew. This likely just indicates that the violation types that are more frequent than others are different across the boroughs.

###### Payment Amount by Violation

```{r}
payment_by_violation <- violation %>% filter(payment_amount != 0)
fig2 <- plot_ly(payment_by_violation, x = ~payment_amount, color = ~violation, type = "box", colors = "viridis")
fig2 %>% layout(yaxis = list(showticklabels = FALSE),
                title = "<b>Payment Amount by Violation Type</b>",
                xaxis = list(title = "Payment Amount"))
```

We see that the distribution of payment amounts can vary significantly between violation types.

###### Fire Hydrant Violation Payment Amount by Borough
```{r}
fire_hydrant_violation_payment <- violation %>% filter(payment_amount != 0, violation == "FIRE HYDRANT")
fig3 <- plot_ly(temp, x = ~payment_amount, color = ~borough, type = "box", colors = "viridis")
fig3 %>% layout(yaxis = list(showticklabels = FALSE),
                title = "<b>Fire Hydrant Payment Amount by Borough</b>",
                xaxis = list(title = "Payment Amount"))
```

Finally, we see here that the distribution of fire hydrant payment amounts is about the same across the five boroughs. It appears that most recipients of this violation will pay at most $115.