---
title: "hydrant_analysis"
output: github_document
---
```{r setup, include=FALSE}
library(tidyverse)
library(httr)
library(rvest)

source("code/data_cleaning.R")
source("code/formatting.R")

```

### Chi-square Test

We want to examine whether the violation types vary among boroughs. We predicted that there is no difference in ticket amounts proportions in violation types in different boroughs. 

We perform the chi-square test to verify our assumption. 

$H_0:$ the proportions of tickets of violation type in five boroughs are equal; 
$H_a:$ there exists at least one borough is different. 

```{r}
## 1) No parking-street cleaning, 2) Failure to display a muni-meter receipt, 3) Inspection sticker-expired/missing, 4) Registration sticker-expired /missing, and 5) Fire hydrant. 

five_common_violation = 
  violation1 %>%
  select(borough, violation) %>% 
  filter(violation %in%
           c("NO PARKING-STREET CLEANING",
             "FAIL TO DSPLY MUNI METER RECPT",
             "INSP. STICKER-EXPIRED/MISSING",
             "REG. STICKER-EXPIRED/MISSING",
             "FIRE HYDRANT")) %>%
  count(violation, borough) %>% 
  pivot_wider(
    names_from = "violation",
    values_from = "n"
  ) %>% 
  data.matrix() %>% 
  subset(select = -c(borough))

rownames(five_common_violation) <- c("Bronx", "Brooklyn", "Manhattan", "Queens", "Staten Island")

five_common_violation %>% 
  knitr::kable(caption = "Results Table")

chisq.test(five_common_violation)

x_crit = qchisq(0.95, 16)
x_crit
```

Interpretation: The result of chi-square shows that $\chi^2 > \chi_{crit}$, at significant level $\alpha = 0.05$, sp we reject the null hypothesis and conclude that there does exist at least one borough's proportion of violation amounts is different from others.  



```{r}
fire_hydrant = violation1 %>% filter(violation == "FIRE HYDRANT")

fire_hydrant_id = violation1 %>% filter(violation == "FIRE HYDRANT") %>% 
  select(issue_date, borough, violation, plate) %>% 
  group_by(plate) %>% 
  filter(n() > 1) %>% 
  distinct(plate) %>% 
  ungroup()
 
 duplicate_hydrant = inner_join(fire_hydrant_id, fire_hydrant, by = "plate")
 
 duplicate_hydrant %>% 
  count(plate) %>% 
   ggplot(aes(x = n)) + 
   geom_histogram()
   
   violation %>% 
     filter(plate == "JRA7539") %>% 
     summarize(sum = sum(amount_due))
```

We want to know whether proportions of the population receives fire hydrant violations in each borough are equal. 

First, we will assume: 
1) Each car has only one driver;
2) Each car gets one fire hydrant violation in 2021

We perform a t-test to see if the mean number of fire hydrant violations is 1. 

```{r}

```

### prop.test
```{r}

url = "https://www.citypopulation.de/en/usa/newyorkcity/"
nyc_population_html = read_html(url)

population = nyc_population_html %>% 
  html_elements(".rname .prio1") %>% 
  html_text()

boro = nyc_population_html %>% 
  html_elements(".rname a span") %>% 
  html_text()

nyc_population = tibble(
  borough = boro,
  population = population %>% str_remove_all(",") %>% as.numeric()
) 
  
fire_hydrant = violation1 %>%
  select(borough, violation, plate) %>% 
  filter(violation == "FIRE HYDRANT") %>%
  distinct(plate, borough) %>% 
  count(borough) 

boro_population = left_join(fire_hydrant, nyc_population)

boro_population %>% 
  knitr::kable(caption = "Results Table")

prop.test(boro_population$n, boro_population$population)

```

The proportions of people getting fire hydrant violations are different across boroughs.