---
title: "Violations by Vehicle Body Type"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
    theme: cosmo
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE, echo = FALSE}
library(tidyverse)
library(mgcv)
library(plotly)

source("code/data_cleaning.R")
source("code/formatting.R")

head(violation)
```

## Frequency of violation by Vehicle Body Type

The plot describes the frequency of violation by vehicle body types. There are mainly top 5 types of vehicle body at the top 5 ranking(unknown type excluded), which are SDN, PICK, 2DSD, 4DSD, SUBN. The type abbreviations are the exact match of the body type listed on the vehicle registration. The law defines a suburban(SUBN) as a vehicle that can be used to carry passengers and cargo. Other common body types and codes for vehicles registered in the passenger vehicle class are sedan (SDN), a two-door sedan (2DSD) and a four-door sedan (4DSD), pick-up trucks (PICK). 
```{r, warning=FALSE, message=FALSE}
violation_df = 
  violation %>%
  count(vehicle_body_type) %>% 
  mutate(
    vehicle_body_type = fct_reorder(vehicle_body_type, n) 
  ) %>% 
  filter(
    vehicle_body_type !="NA",
    n > 10000
  ) %>% 
  ggplot(aes(x = vehicle_body_type, y = n, fill = vehicle_body_type)) +
  geom_bar(stat = "identity") +
  labs(
    title = "Frequency of Violation by Vehicle Body Type",
    x = "Vehicle Body Types",
    y = "Counts"
  ) +
  geom_text(aes(label = n), position = position_dodge(width=0.9), vjust=-0.25)
violation_df

```
