---
title: "fire hydrant analysis"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
    theme: cosmo
---

```{r setup, include=FALSE}
library(tidyverse)
library(httr)
library(rvest)

source("code/data_cleaning.R")
source("code/formatting.R")

```

### Chi-square Test

We want to examine whether the violation types vary among boroughs. We predicted that there is no difference in ticket amounts proportions in violation types in different boroughs. 

We perform the chi-square test to verify our assumption. 

$H_0:$ the proportions of tickets of violation type in five boroughs are equal; 
$H_a:$ there exists at least one borough is different. 

```{r}
## 1) No parking-street cleaning, 2) Failure to display a muni-meter receipt, 3) Inspection sticker-expired/missing, 4) Registration sticker-expired /missing, and 5) Fire hydrant. 

five_common_violation = 
  violation1 %>%
  select(borough, violation) %>% 
  filter(violation %in%
           c("NO PARKING-STREET CLEANING",
             "FAIL TO DSPLY MUNI METER RECPT",
             "INSP. STICKER-EXPIRED/MISSING",
             "REG. STICKER-EXPIRED/MISSING",
             "FIRE HYDRANT")) %>%
  count(violation, borough) %>% 
  pivot_wider(
    names_from = "violation",
    values_from = "n"
  ) %>% 
  data.matrix() %>% 
  subset(select = -c(borough))

rownames(five_common_violation) <- c("Bronx", "Brooklyn", "Manhattan", "Queens", "Staten Island")

five_common_violation %>% 
  knitr::kable(caption = "Results Table")

chisq.test(five_common_violation)

x_crit = qchisq(0.95, 16)
x_crit
```

Interpretation: The result of chi-square shows that $\chi^2 > \chi_{crit}$, at significant level $\alpha = 0.05$, sp we reject the null hypothesis and conclude that there does exist at least one borough's proportion of violation amounts is different from others.  


### Proportion Test

We want to know whether proportions of the population receives fire hydrant violations in each borough are equal. We derived the population of each borough from the most recent [census](https://www.citypopulation.de/en/usa/newyorkcity/). 

First, we will assume: 
1) Each car has only one driver;
2) Each car gets one fire hydrant violation in 2021. 

```{r}

url = "https://www.citypopulation.de/en/usa/newyorkcity/"
nyc_population_html = read_html(url)

population = nyc_population_html %>% 
  html_elements(".rname .prio1") %>% 
  html_text()

boro = nyc_population_html %>% 
  html_elements(".rname a span") %>% 
  html_text()

nyc_population = tibble(
  borough = boro,
  population = population %>% str_remove_all(",") %>% as.numeric()
) 
  
fire_hydrant = violation1 %>%
  select(borough, violation, plate) %>% 
  filter(violation == "FIRE HYDRANT") %>%
  distinct(plate, borough) %>% 
  count(borough) 

boro_population = left_join(fire_hydrant, nyc_population)

boro_population %>% 
  knitr::kable(caption = "Results Table")

prop.test(boro_population$n, boro_population$population)

```

In conclusion, the proportions of people getting fire hydrant violations are different across boroughs. 

### A Fun fact--The Love of Fire Hydrant 

During our analysis process of fire hydrant violation, we found out a license plate `JRA7539` got 85 tickets due to fire hydrant in 2021. It's ridiculous! So we want to find what this car is doing in 2021. The result shows that `JRA7539` got a total of 221 violations with fine amount of $19130 this year. 

```{r}
fire_hydrant = violation1 %>% filter(violation == "FIRE HYDRANT")

fire_hydrant_id = violation1 %>% filter(violation == "FIRE HYDRANT") %>% 
  select(issue_date, borough, violation, plate) %>% 
  group_by(plate) %>% 
  filter(n() > 1) %>% 
  distinct(plate) %>% 
  ungroup()
 
 duplicate_hydrant = inner_join(fire_hydrant_id, fire_hydrant, by = "plate")
 
 duplicate_hydrant %>% 
  count(plate) %>% 
   ggplot(aes(x = n)) + 
   geom_histogram()
   
  violation %>% 
     filter(plate == "JRA7539") %>% 
     count(violation) %>% 
     summarize(sum = sum(n))
 
   violation %>% 
     filter(plate == "JRA7539") %>% 
     summarize(fine = sum(amount_due))
```
