---
title: "parking_covid"
author: "Waveley Qiu (wq2162)"
date: "12/6/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(httr)
library(tidyverse)
library(lubridate)
library(lmtest)
library(patchwork)

source("code/data_cleaning.R")
source("code/formatting.R")
```

The recent COVID-19 pandemic has caused disruptions in many spheres of everyday life, both in legislation as well as in the societal mind. For many, the most tangible 

We believe that parking violations are related to general automotive movement within a given city, as it seems reasonable to assume that the number of parking violations given is directly related to the number of individuals who are commuting to or from places. 

```{r, message=FALSE, warning=FALSE, fig.height = 10, fig.width = 8}

common_violations <-
  violation %>% group_by(violation) %>% count(violation) %>% arrange(-n)

url <- "https://raw.githubusercontent.com/nychealth/coronavirus-data/master/trends/data-by-day.csv"

covid <- 
  read_csv(url(url)) %>%
  janitor::clean_names() %>%
  select(date_of_interest, bx_case_count, mn_case_count, si_case_count, qn_case_count, bk_case_count) %>%
  pivot_longer(
    cols = bx_case_count:bk_case_count,
    names_to = "borough",
    values_to = "new_cases"
  ) %>%
  mutate(
    borough_abbr = str_replace(borough, "_case_count", ""),
    borough = 
      case_when(
      borough_abbr == "bx" ~ "Bronx",
      borough_abbr == "bk" ~ "Brooklyn",
      borough_abbr == "mn" ~ "Manhattan",
      borough_abbr == "qn" ~ "Queens",
      borough_abbr == "si" ~ "Staten Island"
    ),
    date_of_interest = as.Date(date_of_interest, "%m/%d/%Y")
  ) 

violation_covid <-
  violation %>% 
  count(issue_date, borough) %>%
  rename(total_violations = n) %>%
  left_join(covid, by = c("issue_date" = "date_of_interest", "borough"))  %>%
  filter(!is.na(new_cases))
```

First, we will construct a scatter plot of new COVID-19 cases against total violations, colored by borough:

```{r, message=FALSE, warning=FALSE, fig.height = 10, fig.width = 8}
violation_covid %>%
  ggplot(aes(x = new_cases, y = total_violations)) +
  geom_point(alpha = 0.15, aes(col = borough)) +
  geom_smooth(se = FALSE, col = "red") +
  labs(
    x = "New COVID-19 Cases",
    y = "Total Violations",
    col = "Borough",
    title = "Total Violations vs. New COVID-19 Cases (2021)",
    caption = "Note: each point represents a single day of observation"
  )
```

It appears that the greatest range in number of violations given out occurs when there are fewer than about 300 COVID-19 cases a day. 


```{r, fig.height = 10, message=FALSE, warning=FALSE}
violation_covid_long <-
  violation_covid %>% 
  pivot_longer(
    cols = total_violations:new_cases,
    names_to = "parameter",
    values_to = "value"
  ) %>%
  mutate(
    parameter = if_else(parameter == "total_violations", "Total Violations", if_else(parameter == "new_cases", "Total New COVID-19 Cases", ""))
  )


gg_violation_covid <- 
  violation_covid_long %>% 
  ggplot(aes(x = issue_date, y = value, col = parameter)) +
  geom_line(alpha = 0.2) + 
  geom_smooth(se = FALSE) +
  xlim(c(as.Date("01-01-2021", "%m/%d/%Y"), as.Date("11-21-2021", "%m/%d/%Y"))) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  labs(
    x = "Date",
    y  = "Count",
    col = "Parameter"
  )

(gg_violation_covid + 
    labs(title = "Total Parking Violations and New COVID-19 Cases Over Time\n(2021)") +
    theme(legend.position = "none")) / 
(gg_violation_covid  
   + facet_grid(. ~ borough))
```

We will now perform a Granger-causality test to see if knowing the previous day's number of COVID-19 cases is helpful in predicting the number of parking violations given out. We will perform this test at an $\alpha = 0.05$ significance level. 

```{r, message=FALSE, warning=FALSE}
grangertest(total_violations ~ new_cases, order = 1, data = violation_covid)
```

As the test's p-value is less than our predetermined significance level of 0.05, we reject the null hypothesis that  



























